Quality Definitions of Qualities

### 2019-10-23 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Added begin{defn} ... \end{defn} to several definitions

A result is said to be reproducible if another researcher can take the original
code and input data, execute it, and re-obtain the same result (Peng, Dominici,
and Zeger, 2006), as cited in \citet{BenureauAndRougier2017}.

@@

Documentation achieves replicability if the description it provides of the
algorithms is sufficiently precise and complete for an independent researcher to
re-obtain the results it presents.  \citep{BenureauAndRougier2017}

@@

\begin{quotation}
\noindent The ability to meet the needs of the present without compromising the ability of
future generations to meet their own needs \cite{Brundtland1987}.
\end{quotation}

@@

\begin{quotation}
\noindent Technical sustainability has the central objective of long-time
usage of systems and their adequate evolution with changing surrounding
conditions and respective requirements \cite{PenzenstadlerAndHenning2013}.
\end{quotation}

@@

\begin{quotation}
  \noindent Sustainable development is a mindset (principles) and an
  accompanying set of practices that enable a team to achieve and maintain an
  optimal development pace indefinitely~\cite{Tate2005}.
\end{quotation}

@@

\begin{quotation}
  \noindent The concept of sustainability is based on three pillars: the
  ecological, the economical and the social. This means that for a software to
  be sustainable, we must take all of its effects -- direct and indirect -- on
  the environment, the economy and the society into account. In addition, the
  entire life cycle of a software has to be considered: from planning and
  conception to programming, distribution, installation, usage and
  disposal~\cite{Heine2017}.
\end{quotation}

\begin{quotation}
  \noindent The capacity of the software to endure. In other words,
  sustainability means that the software will continue to be available in the
  future, on new platforms, meeting new needs~\cite{Katz2016}.
\end{quotation}

Definition from Neil Chue Hong:
\begin{quotation}
\noindent Sustainable software is software which is:
-- Easy to evolve and maintain
-- Fulfils its intent over time
-- Survives uncertainty
-- Supports relevant concerns (Political, Economic, Social, Technical,
Legal, Environmental)~\cite{Katz2016}.
\end{quotation}

@@

Documented requirements are said to be abstract if they state what the software
must do and the properties it must possess, but do not speak about how these are
to be achieved \citep{GhezziEtAl2003}.

``An abstraction for a software artifact is a succinct description that suppresses
the details that are unimportant to a software developer and emphasizes the
information that is important.'' \cite{Krueger1992}

``Abstraction means that we concentrate on the essential features and ignore,
abstract from, details that are not relevant at the level we are currently
working.''  \cite[p.\ 296]{VanVliet2000}

``Abstraction in mathematics is the process of extracting the underlying essence
of a mathematical concept, removing any dependence on real world objects with
which it might originally have been connected, and generalizing it so that it
has wider applications or matching among other abstract descriptions of
equivalent phenomena.''
\href{https://en.wikipedia.org/wiki/Abstraction_(mathematics)} {Wikipedia
  Definition}

>>>>

\begin{defn}
A result is said to be reproducible if another researcher can take the original
code and input data, execute it, and re-obtain the same result (Peng, Dominici,
and Zeger, 2006), as cited in \citet{BenureauAndRougier2017}.
\end{defn}

@@

\begin{defn}
Documentation achieves replicability if the description it provides of the
algorithms is sufficiently precise and complete for an independent researcher to
re-obtain the results it presents.  \citep{BenureauAndRougier2017}
\end{defn}

@@

\begin{defn}
\noindent The ability to meet the needs of the present without compromising the ability of
future generations to meet their own needs \cite{Brundtland1987}.
\end{defn}

@@

\begin{defn}
\noindent Technical sustainability has the central objective of long-time
usage of systems and their adequate evolution with changing surrounding
conditions and respective requirements \cite{PenzenstadlerAndHenning2013}.
\end{defn}

@@

\begin{defn}
  \noindent Sustainable development is a mindset (principles) and an
  accompanying set of practices that enable a team to achieve and maintain an
  optimal development pace indefinitely~\cite{Tate2005}.
\end{defn}

@@

\begin{defn}
  The concept of sustainability is based on three pillars: the
  ecological, the economical and the social. This means that for a software to
  be sustainable, we must take all of its effects -- direct and indirect -- on
  the environment, the economy and the society into account. In addition, the
  entire life cycle of a software has to be considered: from planning and
  conception to programming, distribution, installation, usage and
  disposal~\cite{Heine2017}.
\end{defn}

\begin{defn}
  \noindent The capacity of the software to endure. In other words,
  sustainability means that the software will continue to be available in the
  future, on new platforms, meeting new needs~\cite{Katz2016}.
\end{defn}

Definition from Neil Chue Hong:
\begin{defn}
Sustainable software is software which is:
-- Easy to evolve and maintain
-- Fulfils its intent over time
-- Survives uncertainty
-- Supports relevant concerns (Political, Economic, Social, Technical,
Legal, Environmental)~\cite{Katz2016}.
\end{defn}

@@

\begin{defn}
Documented requirements are said to be abstract if they state what the software
must do and the properties it must possess, but do not speak about how these are
to be achieved \citep{GhezziEtAl2003}.  
\end{defn}

\begin{defn}
``An abstraction for a software artifact is a succinct description that suppresses
the details that are unimportant to a software developer and emphasizes the
information that is important.'' \cite{Krueger1992}
\end{defn}

\begin{defn}
``Abstraction means that we concentrate on the essential features and ignore,
abstract from, details that are not relevant at the level we are currently
working.''  \cite[p.\ 296]{VanVliet2000}
\end{defn}

\begin{defn}
``Abstraction in mathematics is the process of extracting the underlying essence
of a mathematical concept, removing any dependence on real world objects with
which it might originally have been connected, and generalizing it so that it
has wider applications or matching among other abstract descriptions of
equivalent phenomena.''
\href{https://en.wikipedia.org/wiki/Abstraction_(mathematics)} {Wikipedia
  Definition}
\end{defn}
